The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-01-22 papers/pair-correlation/paper.tex
Added new 2d pair data, and updated the pair plots. I have changed the orientation so that the 2d plot is on the left, rather than above the 1d plot. Waiting on consensus for this layout to make final tweaks. Tested on paho-arch. Took 1:22.36.
More pair-correlation plot tweaks. Tested on paho-arch. Took 0:51.95.

\begin{figure*}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-1.pdf}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{ \paircaption{0.1} \fixme{Fix *ALL* plots to specify units of distance $x/R$.}
  }\label{fig:pair-distribution-1}
\end{figure*}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
%%   \caption{\paircaption{0.2}}\label{fig:pair-distribution-2}
%% \end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{\paircaption{0.3}}\label{fig:pair-distribution-3}
\end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
%%   \caption{\paircaption{0.4}}\label{fig:pair-distribution-4}
%% \end{figure}

@@

\begin{figure*}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-3.pdf}
  \caption{\fixme{Put all triplets together here.  Tweak spacing, add a, b, c, etc.} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-3}
\end{figure*}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.4, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-4}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-inbetween-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-inbetween-distribution-4}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}\\
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{ \paircaption{0.1} \fixme{Fix *ALL* plots to specify units of distance $x/R$.}
  }\label{fig:pair-distribution-1}
\end{figure*}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
%%   \caption{\paircaption{0.2}}\label{fig:pair-distribution-2}
%% \end{figure}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
%   \caption{\paircaption{0.3}}\label{fig:pair-distribution-3}
% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
%%   \caption{\paircaption{0.4}}\label{fig:pair-distribution-4}
%% \end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Put all triplets together here.  Tweak spacing, add a, b, c, etc.} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-3}
\end{figure*}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.4, plotted when
%     $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
%     shows the triplet distribution function, with white corresponding
%     to the contact value of the \emph{pair} distribution function.
%     The plot on the right shows the value of $g^{(3)}$ along the path
%     shown as a dotted line on the plot to the
%     left.}\label{fig:triplet-contact-distribution-4}
% \end{figure}

@@

% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
%     separated by the diameter of one sphere.}\label{fig:triplet-inbetween-distribution-3}
% \end{figure}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-4.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
%     separated by the diameter of one sphere.}\label{fig:triplet-inbetween-distribution-4}
% \end{figure}
